Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-04 Papers/ms.tex
Captions mention the symbols

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{image1.pdf}
\caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
lens close to the center of the image (which does not contribute any flux), plus a
single substructure close to the top left image.
The image was blurred by a PSF and had some noise added.
In an arbitrary system of units, this image extends from -8 to 8 in the
$x$ and $y$ directions.\label{fig:image1}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{image2.pdf}
\caption{{\revisions The `harder' simulated data, consisting of a more
complex source profile, and a lens with 10 substructures.}
\label{fig:image2}}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{image1.pdf}
\caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
lens close to the center of the image, indicated by the white circle, plus a
single substructure close to the top left image (indicated by a star symbol).
The image was blurred by a PSF and had some noise added.
In an arbitrary system of units, this image extends from -8 to 8 in the
$x$ and $y$ directions.\label{fig:image1}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{image2.pdf}
\caption{{\revisions The `harder' simulated data, consisting of a more
complex source profile, and a lens with an SIE+$\gamma$ (whose centre is
indicated by a white circle) and ten substructures. Only five of the
substructures (star symbols) occured within the square image boundary, but the other five still have an effect on the image.}
\label{fig:image2}}
\end{center}
\end{figure}
